\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb, amsmath, amsthm}
\theoremstyle{plain}
\newtheorem*{theorem*}{Theorem}
\newtheorem{theorem}{Theorem}

\usepackage{mathtools}
\renewcommand\qedsymbol{$\blacksquare$}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}

\begin{document}
	
\begin{theorem*}[\textbf{2.4.40}]
    The union of two countable sets is countable.
\end{theorem*}

\begin{proof}
    By cases. Let $A$, and $B$ be countable sets. There are three cases that must be considered. 
    $(i)$ $A$ and $B$ are finite, $(ii)$ exclusively $A$ or $B$ is finite and the other is 
    countably infinite, $(iii)$ $A$ and $B$ are both countably infinite.
    \\ \\
    $(i)$ Suppose $A$ and $B$ are finite. There exist natural numbers $m$, and $n$ such that 
    $|A| = m$ and $|B| = n$. The maximum cardinality for $A \cup B$ occurs when $A$ and $B$ are 
    disjoint, where the cardinality is $m + n$. $m+n$ is a natural number less than $\aleph_0$. 
    Thus, $A \cup B$ is finite and countable by definition. 
    \\ \\
    $(ii)$ Without loss of generality suppose $A$ is finite with cardinality $n$, and $B$ is 
    countably infinite. It must be that a sequence exists $\{a_i\} = \{a_0, a_1, \dots a_n\}$ 
    containing all elements in $A$. Since a bijection exists between $B$ and $\mathbb{N}$ by the 
    definition for countability, a sequence exists $\{b_i\} = \{b_0, b_1, b_2, \dots \}$ containing 
    all elements in $B$. Clearly, for the union of $A$ and $B$ a sequence exists 
    $\{c_i\} = \{a_0, a_1, \dots, a_n, b_0, b_1, b_2, \dots \}$. Infinite sequences are countable 
    by definition, so $A \cup B$ is a countably infinite set.
    \\ \\
    $(iii)$ Suppose $A$ and $B$ are infinitely countable sets. Since the set cardinalities are 
    $\aleph_0$, $A$ and $B$ are bijective with $\mathbb{N}$. Thus, the elements in $A$ can be 
    ordered by the sequence $\{a_i\} = \{a_0, a_1, a_2, \dots\}$, and the elements in $B$ can be 
    ordered by the sequence $\{b_i\} = \{b_0, b_1, b_2, \dots \}$. The union of $A$ and $B$ can be 
    ordered by the sequence $\{c_i\} = \{a_0, b_0, a_1, b_1, a_2, b_2, \dots\}$. Thus a bijection 
    exists between $\mathbb{N}$ and the union of $A$ and $B$, and the cardinality of that union is 
    $\aleph_0$.
\end{proof}

\end{document}
